Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices

### 2023-05-14 manuscript/manuscript.tex
Final Commit, all figs are referenced

The sentiment analysis took approximately 12 minutes to run and the data generated created 3 new columns in the working dataframe: sentiment, label, and score. Score is a numeric value from the range [0,1] where the higher the score the more confident the sentiment analyzed is correct. This score is the confidence that the model gives for the sentiment assignment and serves as a way to observe sentiment as a continuous variable. When combined and observed as a frequency histogram as in Figure~/ref{fig:sentimenthist}, it seems that the sentiment scores for the period are centered around a slightly positive value of 0.1 indicating sentiment for the CVX term was generally positive but normally distributed more or less.

>>>>

The sentiment analysis took approximately 12 minutes to run and the data generated created 3 new columns in the working dataframe: sentiment, label, and score. Score is a numeric value from the range [0,1] where the higher the score the more confident the sentiment analyzed is correct. This score is the confidence that the model gives for the sentiment assignment and serves as a way to observe sentiment as a continuous variable. When combined and observed as a frequency histogram as in Figure~\ref{fig:sentimenthist}, it seems that the sentiment scores for the period are centered around a slightly positive value of 0.1 indicating sentiment for the CVX term was generally positive but normally distributed more or less.
